Structured Versus Decorated Cospans

### 2021-01-02 cospans.tex
Added ref to Christina's unitor in Lemma 4.1

Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
\begin{displaymath}
 \scalebox{.9}
{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
 \end{tikzcd}}
\end{displaymath}
All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
\end{proof}

@@

since the right hand side of the first equation is given by $U_f$ and the right hand side of the second equation is given as in Definition \ref{def:companion}.

>>>>

Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
\begin{equation}\label{eq:decunitor}
 \scalebox{.9}
{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{a,m}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a+1)"'] \&\&  \\
1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
 \end{tikzcd}}
\end{equation}
All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
\end{proof}

@@

since the right hand side of the first equation is given by $U_f$ and the second equation utilizing the left and right unitors of $\odot$, which may be found in (\ref{eq:decunitor}), is given as in Definition \ref{def:companion}.
